---
#title: "Exome assembly stats"
#author: "gwct"
#date: "01/15/2020"
output: 
  html_document:
    includes:
      in_header: '../html-chunks/rmd_header.html'
    df_print: paged
    code_folding: hide
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)

targets = 203198
target_avg_len = 267.5448577249776
target_min_len = 100
target_total_len = 54364580

tiles = 470359
tile_avg_len = 109.8747
tile_min_len = 57
tile_total_len = 51679441
# Target and tile info

htmltools::includeHTML("../html-chunks/nav.html")

```

# Exome mapping stats

```{r readdata, echo=FALSE, warning=FALSE}
new_data = read.csv("../../data/summary-exomes.csv", header=TRUE)
new_data = new_data[!grepl("pos_ctrl", new_data$Label),]
new_data$Batch = as.character(new_data$Batch)
new_data$Prep = as.character(new_data$Prep)

by_library = subset(new_data, !is.na(Prep))
```

## Reads sequenced vs. reads mapped (to Mouse)

```{r fig1, out.width="100%", fig.align = "center", warning=FALSE}
#####################
# # reads vs reads mapped to mouse, colored by sequencing batch
#####################

mapped_p = ggplot(new_data, aes(x=Total.reads, y=Mouse.mapped.reads, color=Batch)) +
  geom_smooth(method="glm", alpha=0, fullrange=T, color="#666666") +
  geom_point(size=2, alpha=0.6) +
  labs(x="# Unfiltered reads", y="# Reads mapped") +
  scale_color_manual(labels=c("Original 40", "Rattus 8", "Mus 14", "New 70", "Aussie 46"),
                     values=c("#920000", "#333333", "#006ddb", "#db6d00", "#b66dff")) +
  
  theme_classic() +
  guides(colour = guide_legend(override.aes = list(size=4))) +
  theme(axis.text=element_text(size=12), 
        axis.title=element_text(size=16), 
        axis.title.y=element_text(margin=margin(t=0,r=10,b=0,l=0),color="black"), 
        axis.title.x=element_text(margin=margin(t=10,r=0,b=0,l=0),color="black"),
        axis.line=element_line(colour='#595959',size=0.75),
        axis.ticks=element_line(colour="#595959",size = 1),
        axis.ticks.length=unit(0.2,"cm"),
        legend.position="right",
        legend.text=element_text(size=14),
        #legend.spacing.x=unit(1, 'cm'),
        legend.title=element_text(size=14, face="bold"),
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(0,-10,0,-10),
        
        legend.key.size = unit(1.5, 'lines'),
        plot.title = element_text(hjust=0.5, size=20),
        plot.margin = unit(c(0.5,0.5,0.5,0.5), "cm")
  ) 
print(mapped_p)
```

---

## Reads sequenced vs. reads mapped (to Rat)

```{r fig2, out.width="100%", fig.align = "center", warning=FALSE}
#####################
# # reads vs reads mapped to rat, colored by sequencing batch
#####################

mapped_p = ggplot(new_data, aes(x=Total.reads, y=Rat.mapped.reads, color=Batch)) +
  geom_smooth(method="glm", alpha=0, fullrange=T, color="#666666") +
  geom_point(size=2, alpha=0.6) +
  labs(x="# Unfiltered reads", y="# Reads mapped") +
  scale_color_manual(labels=c("Original 40", "Rattus 8", "Mus 14", "New 70", "Aussie 46"),
                     values=c("#920000", "#333333", "#006ddb", "#db6d00", "#b66dff")) +
  
  theme_classic() +
  guides(colour = guide_legend(override.aes = list(size=4))) +
  theme(axis.text=element_text(size=12), 
        axis.title=element_text(size=16), 
        axis.title.y=element_text(margin=margin(t=0,r=10,b=0,l=0),color="black"), 
        axis.title.x=element_text(margin=margin(t=10,r=0,b=0,l=0),color="black"),
        axis.line=element_line(colour='#595959',size=0.75),
        axis.ticks=element_line(colour="#595959",size = 1),
        axis.ticks.length=unit(0.2,"cm"),
        legend.position="right",
        legend.text=element_text(size=14),
        #legend.spacing.x=unit(1, 'cm'),
        legend.title=element_text(size=14, face="bold"),
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(0,-10,0,-10),
        
        legend.key.size = unit(1.5, 'lines'),
        plot.title = element_text(hjust=0.5, size=20),
        plot.margin = unit(c(0.5,0.5,0.5,0.5), "cm")
  )
print(mapped_p)
```

---

## Total reads vs. mapped reads compared between mouse and rat mappings

```{r fig3, out.width="100%", fig.align = "center", warning=FALSE}
#####################
# # reads vs mapped reads
#####################

map_comp = ggplot(new_data, aes(x=Total.reads, y=Mouse.mapped.reads)) +
  geom_segment(x=new_data$Total.reads, y=new_data$Mouse.mapped.reads, xend=new_data$Total.reads, yend=new_data$Rat.mapped.reads) +
  geom_smooth(method="glm", alpha=0, fullrange=T, color="#666666") +
  geom_smooth(aes(x=Total.reads, y=Rat.mapped.reads), method="glm", alpha=0, fullrange=T, color="#ff9933") +
  geom_point(aes(color="Mouse"), size=2, alpha=0.6) +
  geom_point(aes(x=Total.reads, y=Rat.mapped.reads, color="Rat"), size=2, alpha=0.6) +

  scale_x_continuous(expand=c(0,0), limits=c(1e7,8.5e7)) +
  labs(x="# Unfiltered reads", y="# Reads mapped") +
  
  scale_color_manual(name="Mapped to: ", values=c("Mouse"="#333333", "Rat"="#db6d00")) +
  
  theme_classic() +
  guides(colour = guide_legend(override.aes = list(size=4))) +
  theme(axis.text=element_text(size=12), 
        axis.title=element_text(size=16), 
        axis.title.y=element_text(margin=margin(t=0,r=10,b=0,l=0),color="black"), 
        axis.title.x=element_text(margin=margin(t=10,r=0,b=0,l=0),color="black"),
        axis.line=element_line(colour='#595959',size=0.75),
        axis.ticks=element_line(colour="#595959",size = 1),
        axis.ticks.length=unit(0.2,"cm"),
        legend.position="bottom",
        legend.text=element_text(size=14),
        #legend.spacing.x=unit(1, 'cm'),
        legend.title=element_text(size=14, face="bold"),
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(0,-10,0,-10),
        legend.key.size = unit(1.5, 'lines'),
        plot.title = element_text(hjust=0.5, size=20),
        plot.margin = unit(c(0.5,0.5,0.5,0.5), "cm")
  )
print(map_comp)
```

---

## Reads sequenced vs. depth (mapped to Mouse)

```{r fig4, out.width="100%", fig.align = "center", warning=FALSE}
#####################
# # reads vs read depth to mouse, colored by sequencing batch
#####################

depth_reg = lm(new_data$Mouse.target.depth ~ new_data$Total.reads)

depth_p = ggplot(new_data, aes(x=Total.reads, y=Mouse.target.depth, color=Batch)) +
  geom_smooth(method="glm", alpha=0, fullrange=T, color="#666666") +
  geom_smooth(data=by_library, aes(x=Total.reads, y=Mouse.target.depth), method="glm", alpha=0, fullrange=T, color="#666666", linetype="dashed") +
  geom_point(size=2, alpha=0.6) +
  labs(x="# Unfiltered reads", y="Avg. read depth") +
  scale_color_manual(labels=c("Original 40", "Rattus 8", "Mus 14", "New 70", "Aussie 46"),
                     values=c("#920000", "#333333", "#006ddb", "#db6d00", "#b66dff")) +
  theme_classic() +
  guides(colour = guide_legend(override.aes = list(size=4))) +
  theme(axis.text=element_text(size=12), 
        axis.title=element_text(size=16), 
        axis.title.y=element_text(margin=margin(t=0,r=10,b=0,l=0),color="black"), 
        axis.title.x=element_text(margin=margin(t=10,r=0,b=0,l=0),color="black"),
        axis.line=element_line(colour='#595959',size=0.75),
        axis.ticks=element_line(colour="#595959",size = 1),
        axis.ticks.length=unit(0.2,"cm"),
        legend.position="right",
        legend.text=element_text(size=14),
        #legend.spacing.x=unit(1, 'cm'),
        legend.title=element_text(size=14, face="bold"),
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(0,-10,0,-10),
        
        legend.key.size = unit(1.5, 'lines'),
        plot.title = element_text(hjust=0.5, size=20),
        plot.margin = unit(c(0.5,0.5,0.5,0.5), "cm")
  )
print(depth_p)

cat("Slope", coef(depth_reg)[2], sep=" ")
```

---

## Reads sequenced vs. depth (mapped to Rat)

```{r fig5, out.width="100%", fig.align = "center", warning=FALSE}
#####################
# # reads vs read depth to rat, colored by sequencing batch
#####################

depth_reg = lm(new_data$Rat.target.depth ~ new_data$Total.reads)

depth_p = ggplot(new_data, aes(x=Total.reads, y=Rat.target.depth, color=Batch)) +
  geom_smooth(method="glm", alpha=0, fullrange=T, color="#666666") +
  geom_smooth(data=by_library, aes(x=Total.reads, y=Rat.target.depth), method="glm", alpha=0, fullrange=T, color="#666666", linetype="dashed") +
  geom_point(size=2, alpha=0.6) +
  labs(x="# Unfiltered reads", y="Avg. read depth") +
  scale_color_manual(labels=c("Original 40", "Rattus 8", "Mus 14", "New 70", "Aussie 46"),
                     values=c("#920000", "#333333", "#006ddb", "#db6d00", "#b66dff")) +
  theme_classic() +
  guides(colour = guide_legend(override.aes = list(size=4))) +
  theme(axis.text=element_text(size=12), 
        axis.title=element_text(size=16), 
        axis.title.y=element_text(margin=margin(t=0,r=10,b=0,l=0),color="black"), 
        axis.title.x=element_text(margin=margin(t=10,r=0,b=0,l=0),color="black"),
        axis.line=element_line(colour='#595959',size=0.75),
        axis.ticks=element_line(colour="#595959",size = 1),
        axis.ticks.length=unit(0.2,"cm"),
        legend.position="right",
        legend.text=element_text(size=14),
        #legend.spacing.x=unit(1, 'cm'),
        legend.title=element_text(size=14, face="bold"),
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(0,-10,0,-10),
        
        legend.key.size = unit(1.5, 'lines'),
        plot.title = element_text(hjust=0.5, size=20),
        plot.margin = unit(c(0.5,0.5,0.5,0.5), "cm")
  )
print(depth_p)

cat("Slope", coef(depth_reg)[2], sep=" ")
```

---

## Total reads vs. read depth compared between mouse and rat mappings

```{r fig6, out.width="100%", fig.align = "center", warning=FALSE}
#####################
# # reads vs depth compared between mouse and rat
#####################

depth_comp = ggplot(new_data, aes(x=Total.reads, y=Mouse.target.depth)) +
  geom_segment(x=new_data$Total.reads, y=new_data$Mouse.target.depth, xend=new_data$Total.reads, yend=new_data$Rat.target.depth) +
  geom_smooth(method="glm", alpha=0, fullrange=T, color="#666666") +
  geom_smooth(aes(x=Total.reads, y=Rat.target.depth), method="glm", alpha=0, fullrange=T, color="#ff9933") +
  geom_point(aes(color="Mouse"), size=2, alpha=0.6) +
  geom_point(aes(x=Total.reads, y=Rat.target.depth, color="Rat"), size=2, alpha=0.6) +

  scale_x_continuous(expand=c(0,0), limits=c(1e7,8.5e7)) +
  labs(x="# Unfiltered reads", y="# Reads mapped") +
  
  scale_color_manual(name="Mapped to: ", values=c("Mouse"="#333333", "Rat"="#db6d00")) +
  
  theme_classic() +
  guides(colour = guide_legend(override.aes = list(size=4))) +
  theme(axis.text=element_text(size=12), 
        axis.title=element_text(size=16), 
        axis.title.y=element_text(margin=margin(t=0,r=10,b=0,l=0),color="black"), 
        axis.title.x=element_text(margin=margin(t=10,r=0,b=0,l=0),color="black"),
        axis.line=element_line(colour='#595959',size=0.75),
        axis.ticks=element_line(colour="#595959",size = 1),
        axis.ticks.length=unit(0.2,"cm"),
        legend.position="bottom",
        legend.text=element_text(size=14),
        #legend.spacing.x=unit(1, 'cm'),
        legend.title=element_text(size=14, face="bold"),
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(0,-10,0,-10),
        legend.key.size = unit(1.5, 'lines'),
        plot.title = element_text(hjust=0.5, size=20),
        plot.margin = unit(c(0.5,0.5,0.5,0.5), "cm")
  )
print(depth_comp)
```

---

## Reads sequenced vs. depth (mapped to mouse) by library prep (70 new samples only)

```{r fig7, out.width="100%", fig.align = "center", warning=FALSE}
#####################
# # reads vs read depth to mouse, colored by library prep, 70 new samples only
#####################

depth_reg_new = lm(by_library$Mouse.target.depth ~ by_library$Total.reads)

depth_p = ggplot(by_library, aes(x=Total.reads, y=Mouse.target.depth, color=Prep)) +
  geom_smooth(method="glm", alpha=0, fullrange=T, color="#666666", linetype="dashed") +
  geom_point(size=2, alpha=0.6) +
  labs(x="# Unfiltered reads", y="Avg. read depth") +
  scale_color_manual(labels=c("1", "2", "3"),
                     values=c("#ff6db6", "#24ff24", "#009292"),
                     na.translate=FALSE) +
  theme_classic() +
  guides(colour = guide_legend(override.aes = list(size=4))) +
  theme(axis.text=element_text(size=12), 
        axis.title=element_text(size=16), 
        axis.title.y=element_text(margin=margin(t=0,r=10,b=0,l=0),color="black"), 
        axis.title.x=element_text(margin=margin(t=10,r=0,b=0,l=0),color="black"),
        axis.line=element_line(colour='#595959',size=0.75),
        axis.ticks=element_line(colour="#595959",size = 1),
        axis.ticks.length=unit(0.2,"cm"),
        legend.position="bottom",
        legend.text=element_text(size=14),
        #legend.spacing.x=unit(1, 'cm'),
        legend.title=element_text(size=14, face="bold"),
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(0,-10,0,-10),
        
        legend.key.size = unit(1.5, 'lines'),
        plot.title = element_text(hjust=0.5, size=20),
        plot.margin = unit(c(0.5,0.5,0.5,0.5), "cm")
  )
print(depth_p)

cat("Slope", coef(depth_reg_new)[2], sep=" ")
```

---

## Read depth (mapped to mouse) by library prep (70 new samples only)

```{r fig8, out.width="100%", fig.align = "center", warning=FALSE}
#####################
# # read depth to mouse, colored by library prep, 70 new samples only
#####################
depth_bp = ggplot(by_library, aes(x=Prep, y=Mouse.target.depth, fill=Prep)) +
  geom_boxplot(outlier.shape=NA) + 
  geom_jitter(width=0.1, size=2, alpha=0.6) +
  labs(x="Library prep", y="Avg. read depth") +
  scale_fill_manual(labels=c("1", "2", "3"),
                     values=c("#ff6db6", "#24ff24", "#009292"),
                     na.translate=FALSE) +
  theme_classic() +
  guides(colour = guide_legend(override.aes = list(size=4))) +
  theme(axis.text=element_text(size=12), 
        axis.title=element_text(size=16), 
        axis.title.y=element_text(margin=margin(t=0,r=10,b=0,l=0),color="black"), 
        axis.title.x=element_text(margin=margin(t=10,r=0,b=0,l=0),color="black"),
        axis.line=element_line(colour='#595959',size=0.75),
        axis.ticks=element_line(colour="#595959",size = 1),
        axis.ticks.length=unit(0.2,"cm"),
        legend.position="none",
        legend.text=element_text(size=14),
        #legend.spacing.x=unit(1, 'cm'),
        legend.title=element_text(size=14, face="bold"),
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(0,-10,0,-10),
        
        legend.key.size = unit(1.5, 'lines'),
        plot.title = element_text(hjust=0.5, size=20),
        plot.margin = unit(c(0.5,0.5,0.5,0.5), "cm")
  )
print(depth_bp)
```

```{r footer}
cat("Page last updated:", format(Sys.time(), "%m/%d/%Y %H:%M:%S %Z"))
htmltools::includeHTML("../html-chunks/rmd_footer.html")
```
